A Logical Solution of the Linearity Challenge

### 2025-11-30 paper/Permutations.lagda.tex
++

This definition is essentially the same as the notion of list permutation in
Agda's standard library. Each constructor represents a particular kind of
permutation: \AgdaInductiveConstructor{refl} for the trivial permutation that
does not change anything; \AgdaInductiveConstructor{swap} for the permutation
that swaps the first two elements of a typing context;
\AgdaInductiveConstructor{prep} for the permutation that applies a
sub-permutation to the tail of a typing context;
\AgdaInductiveConstructor{trans} for the sequential composition of permutations.
%
We have preferred defining our own notion of permutation for simplicity: the
\AgdaInductiveConstructor{swap} constructor does not need a sub-permutation for
the tail of the typing context, which can always be performed, if needed, using
\AgdaInductiveConstructor{prep} and \AgdaInductiveConstructor{trans}. Also, and
more importantly, this definition is \emph{monomorphic} (it does not need to
operate on lists of arbitrary type), resulting in a more streamlined usage in
the rest of the code.

>>>>

This definition is essentially the same as the notion of list permutation in
Agda's standard library. Each constructor represents a particular kind of
permutation: \AgdaInductiveConstructor{refl} for the trivial permutation that
does not change anything; \AgdaInductiveConstructor{swap} for the permutation
that swaps the first two elements of a typing context;
\AgdaInductiveConstructor{prep} for the permutation that applies a permutation
to the tail of a typing context; \AgdaInductiveConstructor{trans} for the
sequential composition of permutations.
%
We have preferred defining our own notion of permutation for simplicity: the
\AgdaInductiveConstructor{swap} constructor does not need a sub-permutation for
the tail of the typing context, which can always be performed, if needed, using
\AgdaInductiveConstructor{prep} and \AgdaInductiveConstructor{trans}. Also, and
more importantly, this definition is \emph{monomorphic} (it does not need to
operate on lists of arbitrary type), resulting in a more streamlined usage in
the rest of the code.
